---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dycon: Dyadic Models of Consonance

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

`dycon` is an R package that implements three dyadic models of consonance:

- Hutchinson & Knopoff (1978)
- Sethares (1993)
- Vassilakis (2001)

## Installation

You can install the current version of dycon from Github as follows:

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("dycon")
```

## Usage

These functions take two vectors as input:

- a vector of frequencies, each corresponding to a spectral component;
- a vector of amplitudes, each corresponding to a spectral component.

For analysing musical chords,
it's necessary to expand the notes of the musical 
chord into their implied spectral components.
The `incon` package provides a useful wrapper for these functions
that automatically applies this expansion.

For analysing real audio,
it's necessary to compute the acoustic spectrum
(using e.g. a Fourier Transform)
and then identify the spectral components using a peak-picking algorithm.
See the MIR Toolbox or the Essentia library for such implementations.

```{r}
library(dycon)

f <- c(440, 460, 520) # frequencies
a <- c(1, 1.5, 1) # amplitudes

roughness_hutch(f, a)
roughness_seth(f, a)
roughness_vass(f, a)
```
